ms_figures

### 2018-02-21 man/ms_figures.Rmd
change site names

themeR <- list(
  geom_errorbar(width=.1, position = pd),
  geom_point(position = pd),
  theme_bw(),
  facet_wrap(~vari, labeller = labeller(vari = variables), scales="free_y"),
  xlab(''), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    strip.text = element_text(face="bold", size = 14),
    axis.title.y = element_text(face="bold", size = 14),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),
  scale_shape_manual(values=c(19, 21, 17, 22, 15)),
  scale_color_manual(values=c('black', "blue", 'black','blue','blue')),
  scale_fill_manual(values=c('black', 'white', 'black','white','blue')),
  scale_linetype_manual(values=c("solid","solid","solid","solid", "solid")),
  scale_size_manual(values=c(2,2,2.5, 2.5, 2.5)),
  geom_text(aes(label=Letter, y=postext), 
            position=pd, 
            show.legend = FALSE, size = 3) 
  # , position_jitterdodge(dodge.width = 0.6, jitter.width = .2)
  # geom_text_repel( 
  #                 nudge_x = - 0.5,
  #                 nudge_y = 0.01,
  #                 direction="both", 
  #                 size = 3.5, show.legend = FALSE,
  #                 segment.size = 0.5, 
  #                 segment.alpha = 0.5) 
)

@@

>>>>

themeR <- list(
  geom_errorbar(width=.1, position = pd),
  geom_point(position = pd),
  theme_bw(),
  facet_wrap(~vari, labeller = labeller(vari = variables), scales="free_y"),
  xlab(''), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    strip.text = element_text(face="bold", size = 14),
    axis.title.y = element_text(face="bold", size = 14),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),
  scale_shape_manual(
    values=c("N" = 19, "S" = 21, "CA-High"=22, "CA-Low" = 15, "SJ" = 17)), 
  scale_color_manual(
    values=c("N" = 'black',"S" = "blue", "CA-High" = 'blue', "CA-Low" = 'blue', "SJ" = 'black')),
  scale_fill_manual(
    values=c("N" = 'black', "S" = "white", "CA-High" = 'white', "CA-Low" = 'blue', "SJ" = 'black')),
  scale_linetype_manual(values=c("solid","solid","solid","solid", "solid")),
  scale_size_manual(
    values=c("N" = 2, "S" = 2, "CA-High"=2.5, "CA-Low" = 2.5, "SJ" = 2.5)),
  geom_text(aes(label=Letter, y=postext), 
            position=pd, 
            show.legend = FALSE, size = 3) 
  # , position_jitterdodge(dodge.width = 0.6, jitter.width = .2)
  # geom_text_repel( 
  #                 nudge_x = - 0.5,
  #                 nudge_y = 0.01,
  #                 direction="both", 
  #                 size = 3.5, show.legend = FALSE,
  #                 segment.size = 0.5, 
  #                 segment.alpha = 0.5) 
)

@@

m <- m %>% mutate(site = as.factor(
  case_when(
  site == "caH" ~ "CA-High",
  site == "caL" ~ "CA-Low",
  TRUE ~ site
)))
